\documentclass[xetex,11pt,a4paper]{moderncv}
\usepackage{xltxtra}
\usepackage{polyglossia}
\moderncvstyle{classic}
\moderncvcolor{black}
\usepackage[left=2.0cm,top=2.5cm,right=3cm,bottom=2cm]{geometry}
%\defbibheading{none}{}
\usepackage{lastpage}
%\usepackage{lingulista}
\usepackage[
    natbib=true,
    style=authoryear-ibid,
    maxnames=2,
    hyperref=true,
    sortcites=true,
    firstinits=true,
    bibstyle=authoryear,
    isbn=false,doi=false,
    maxbibnames=15,
    opcittracker=true,
    loccittracker=true,
    terseinits=true,
    sorting=ydnt,
    labelnumber=true,
    backend=bibtex
    ]{biblatex}
\input{/home/mattis/library/latex/tex/lingulist/bibstyle}
\usepackage{enumitem}
\setlength{\bibhang}{\leftmargin}
\addtolength{\bibhang}{0.5cm}
\defbibenvironment{bibliography}
{\list{}
{\setlength{\leftmargin}{\bibhang}%
\setlength{\itemindent}{-\bibhang}%
\setlength{\itemsep}{\bibitemsep}%
\setlength{\parsep}{\bibparsep}}}
{\endlist}
{\item}

\bibliography{/home/mattis/Dropbox/evobib/basic}

\setlength{\bibhang}{20pt}

\setmainlanguage{german}

\setmainfont[Mapping=tex-text]{Arial}
\setsansfont[Mapping=tex-text]{Arial}
\setmonofont{FreeMono}
\newfontfamily{\hana}{HAN NOM A}

\firstname{Johann-Mattis}
\familyname{List}
\title{Lebenslauf}
\address{Frankfurter Str. 17a}{35037 Marburg}
%\mobile{0170/5302738}
\phone{+49-6421-28-25075}
\email{mattis.list@uni-marburg.de}
\homepage{http://lingulist.de}
%\photo{inga.jpg}
%\renewcommand{\firstnamefont}{\fontsize{12}{14}\sffamily\mdseries\upshape}
%\renewcommand{\titlefont}{\Large\sffamily\mdseries\slshape}

\newlength{\mywidth}
\setlength{\mywidth}{14.25cm}

\makeatletter

%\renewcommand*{\section}{sm}{%
%  \par\addvspace{2.5ex}%
%  \phantomsection{}% reset the anchor for hyperrefs
%  \addcontentsline{toc}{section}{#2}%
%  \parbox[t]{\hintscolumnwidth}{\strut\raggedleft\raisebox{\baseletterheight}{\color{color1}\rule{\hintscolumnwidth}{0.95ex}}}%
%  \hspace{\separatorcolumnwidth}%
%  \parbox[t]{\maincolumnwidth}{\strut\sectionstyle{#2}}%
%  \par\nobreak\addvspace{1ex}\@afterheading}% to avoid a pagebreak after the heading


          \fancypagestyle{plain}{%
	  \fancyhead[r]{\addressfont\itshape\strut Page\ \thepage\ of\ \pageref{LastPage}}
	  \fancyhead[l]{\footnotesize J.-M. List -- Curriculumn Vitae und
	  Publication List}
	    \fancyfoot[r]{ }
	    }
\renewcommand*{\cventry}[7][.25em]{%
  \cvitem[#1]{#2}{%
    {\bfseries#3}%
    \ifthenelse{\equal{#4}{}}{}{, {#4}}%
    \ifthenelse{\equal{#5}{}}{}{, #5}%
    \ifthenelse{\equal{#6}{}}{}{, #6}%
    .\strut%
    \ifx&#7&%
      \else{\newline{}\begin{minipage}[t]{\mywidth}\small#7\end{minipage}}\fi}}

\renewcommand*{\cvitem}[3][.25em]{%
  \begin{tabular}{@{}p{\hintscolumnwidth}@{\hspace{\separatorcolumnwidth}}p{\mywidth}@{}}%
    \raggedright\hintstyle{\normalsize #2} &{\normalsize #3}%
  \end{tabular}%
  \par\addvspace{#1}}


\renewcommand*{\cvdoubleitem}[5][.25em]{%
 \cvitem[#1]{#2}{%
   \begin{minipage}[t]{\mywidth}#3\end{minipage}%
   \hfill% fill of \separatorcolumnwidth
   \begin{minipage}[t]{\hintscolumnwidth}\raggedright\hintstyle{#4}\end{minipage}%
   \hspace*{\separatorcolumnwidth}%
   \begin{minipage}[t]{\doubleitemmaincolumnwidth}#5\end{minipage}}}

\RenewDocumentCommand{\section}{sm}{%
  \par\addvspace{2.5ex}%
  \phantomsection{}% reset the anchor for hyperrefs
  \addcontentsline{toc}{section}{#2}%
  \textbf{\normalsize #2}
  %\parbox[t]{\hintscolumnwidth}{\strut\raggedleft\raisebox{\baseletterheight}{\color{color1}\rule{\hintscolumnwidth}{2pt}}}%
  %\hspace{\separatorcolumnwidth}%
  %\parbox[t]{\maincolumnwidth}{\strut \textbf{#2}}%
  \par\nobreak\addvspace{1ex}\@afterheading}% to avoid a pagebreak after the heading       

\makeatother


\usepackage{zhspacing}
\setlength{\hintscolumnwidth}{2.5cm} 
%\setlength{\maincolumnwidth}{12cm}% if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{12.0cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
%\setlength{\listitemmaincolumnwidth}{12cm}
%\setlength{\listdoubleitemmaincolumnwidth}{12cm}
%\setlength{\doubleitemmaincolumnwidth}{12cm}
\setlength{\textwidth}{17cm}
\setlength{\linewidth}{6cm}
% pagestyle settings
%\usepackage{scrpage2}
%\pagestyle{scrheadings}
%\ihead{\scriptsize\em J.-M. List -- Lebenslauf}
%%\chead{}
%\ohead{\scriptsize\em page \pagemark\ of \pageref{LastPage}}
%\ifoot{}
%\cfoot{}
%\ofoot{}


%\fancypagestyle{plain}{%
%\fancyhf{} 
%\fancyhead[R]{\thepage}
%\fancyfoot{}
%\rewnewcommand{\headrulewidth=2pt}}

\renewcommand*{\namefont}{\bfseries\large}
\renewcommand*{\titlefont}{\bfseries\large}
\renewcommand*{\addressfont}{\small}
\renewcommand*{\quotefont}{\large\slshape}

\begin{document}
\pagestyle{plain}
%\defbibenvironment{bibliography}
%{\list{}
%{\setlength{\leftmargin}{0.75cm+\bibhang}%
%\setlength{\itemindent}{-0.75cm}%
%\setlength{\itemsep}{\bibitemsep}%
%\setlength{\parsep}{\bibparsep}}}
%{\endlist}
%{\item[ ]}


%\noindent\bf Johann-Mattis List -- Lebenslauf und Publikationsliste \\
%\noindent\rule{\textwidth}{0.2pt}
\textbf{Johann-Mattis List -- Curriculum Vitae and Publication List}\\ 
\noindent\begin{tabbing}
    gener.formation \= and \kill
    \footnotesize Date of Birth:                      \> 16.07.1981 \\
    \footnotesize Place of Birth:                      \> Kassel \\
    \footnotesize Address:                         \> Frankfurter Str. 17a \\
    \footnotesize                                  \> 35037 Marburg \\
    \footnotesize Telephone:                        \> +49-6421-28-25075 \\
    \footnotesize Email:                           \> \url{mattis.list@uni-marburg.de} \\
    \footnotesize Website:\> \url{http://lingulist.de}\\
\end{tabbing}
\section{Education}
%\cventry{seit 10/2012}{Wissenschaftlicher Mitarbeiter (Post-Doc)}{Ph
\cventry{{\footnotesize 06/02/2013}}{PhD}{Heinrich Heine Universität}{Düsseldorf}{\textit{summa cum
laude}}{Disputatio in General Linguistics}{}
\cventry{{\footnotesize 02/2009--08/2012}}{Doctoral Studies}{Heinrich Heine
Universität}{Düsseldorf}{}{Topic ``Sequence Comparison in Historical
Linguistics".}{}
%\cventry{10/2008--01/2008}{Promotionsstudium}{Freie
%Universität}{Berlin}{}{Vorbereitung der Promotion im Fach Sinologie mit dem
%Thema ``A Phonological Analysis of Yáng Xióng's {\em Fāngyán}".}{}
\cventry{{\footnotesize 25/06/2008}}{Magister Artium}{Freie Universität /
Humboldt-Universität}{Berlin}{\textit{1,0}}{Master degree in Comparative and Indo-European
Linguistics (major) and Sinology and Russian Philology (minors).}{}
\cventry{{\footnotesize 09/2007--01/2008}}{Visiting Student}{Fúdàn
University}{Shànghǎi}{}{Courses in historical linguistics and General and Applied Lingusitics,
Institute for Chines Language and Literature ({\hana 中國語言文學系}).}
\cventry{{\footnotesize 09/2005--07/2006}}{Language Student}{Fúdàn
University}{Shànghǎi}{}{Chinese language courses (advanced level)}{}
\cventry{{\footnotesize 10/2003--09/2008}}{Master (Magister) Studies}{Freie Universität /
Humboldt-Universität}{Berlin}{}{Comparative and Indo-European
Linguistics (major) and Sinology and Russian Philology (minors).}{}
\cventry{{\footnotesize 10/2002--09/2003}}{Master (Magister) Studies}{Eberhard-Karls
Universität}{Tübingen}{}{Rhetorics (major), Comparatistics and Russian Philology (minors).}{}
\cventry{{\footnotesize 19/06/2001}}{Abitur (Highschool Diploma)}{Gymnasium
Carolinum}{Osnabrück}{\textit{1,6}}{Highschool Diploma, with Latin, Chemistry, History, and Music as
main subjects.}{}
 
\section{PhD Thesis}
\cvitem{{\footnotesize Title}}{\em Sequence Comparison in Historical Linguistics} 
\cvitem{{\footnotesize Supervisors}}{Prof. Dr. Hans Geisler, Dr. Wiebke Petersen}
\cvitem{{\footnotesize Description}}{\small The thesis introduces new methods for automatic phonetic alignment and automatic cognate detection.}

\section{Magister Thesis}
\cvitem{{\footnotesize Title}}{\em Rekonstruktion der Aussprache des Mittel- und
Altchinesischen. Vergleich der Rekonstruktionsmethoden der indogermanischen und
der chinesischen Sprachwissenschaft {\em [Reconstruction of the pronunciation of Middle and Old Chinese.
Comparison of the reconstruction methods in Indo-European and Chinese linguistics]}} 
\cvitem{{\footnotesize Supervisors}}{Prof. Dr. Michael Meier-Brügger, Dr. Ingo Schäfer}
\cvitem{{\footnotesize Description}}{\small The thesis deals with the methods that are applied in order to reconstruct unattested stages of ancestral
languages in Indo-European and Chinese linguistics..}
\section{Research}
\cventry{{\footnotesize since 10/2012}}{Research Assistant}{Philipps-Universität}{Marburg}{}{Research
assistant (post-doc) in the ERC-funded research project ``Quantitative Language Comparison" at the
Research Center Deutscher Sprachatlas.}
\cventry{{\footnotesize 02/2009--09/2012}}{Research Assistant}{Heinrich Heine
Universität}{Düsseldorf}{}{Research assistant (doctoral student) in the BMBF-funded research project
``Classification and Evolution in Biology, Linguistics, and the History of Science".}
\section{Teaching}
\input{courses.tex}
%\cventry{{\footnotesize SoSe 2014}}{Seminar}{Philipps-Universität}{Marburg}{}{Seminar ``Chinesische
%Dialektologie", gehalten am Fachbereich für Germanistik und Kunstwissenschaften.}{}{}
%
%\cventry{{\footnotesize SoSe 2014}}{Seminar}{Heinrich Heine Universität}{Düsseldorf}{}{Seminar ``Lautwandel",
%gehalten am Institut für Sprache und Information.}{}{}
%
%\cventry{{\footnotesize WiSe 2013}}{Seminar}{Philipps-Universität}{Marburg}{}{Seminar ``Theoretische und praktische
%Aspekte der quantitativen historischen Linguistik", gehalten am Fachbereich für Germanistik und Kunstwissenschaften.}{}{}
%\cventry{{\footnotesize SoSe 2013}}{Seminar}{Philipps-Universität}{Marburg}{}{Seminar
%``Digital Humanities: Einführung in die maschinelle Sprachverarbeitung" (zusammen mit M. Cysouw),
%gehalten am Fachbereich für Germanistik und Kunstwissenschaften.}{}{}
%\cventry{{\footnotesize SoSe 2013}}{Seminar}{Heinrich Heine Universität}{Düsseldorf}{}{Seminar ``Phonologie der
%chinesischen Dialekte -- Synchrone und diachrone Aspekte", gehalten am Institut für Sprache und
%Information.}{}{}
%\cventry{{\footnotesize WiSe 2012}}{Seminar}{Heinrich Heine Universität}{Düsseldorf}{}{Seminar ``Neue Ansätze in der
%historischen Linguistik", gehalten am Institut für Sprache und Information.}{}{}
%\cventry{{\footnotesize WiSe 2011}}{Doktorandenseminar}{Heinrich Heine Universität}{Düsseldorf}{}{``LaTeX I und II",
%gehalten am Institut für Sprache und Information im Rahmen des SFB 991.}{}{}
%\cventry{{\footnotesize WiSe 2011}}{Seminar}{Heinrich Heine Universität}{Düsseldorf}{}{Seminar ``Geschichte der
%Sprachwissenschaft", gehalten am Institut für Sprache und Information.}{}{}
%\cventry{{\footnotesize SoSe 2011}}{Seminar}{Heinrich Heine Universität}{Düsseldorf}{}{Seminar ``Python", gehalten
%am Institut für Sprache und Information.}{}{}
%\cventry{{\footnotesize WiSe 2010}}{Seminar}{Heinrich Heine Universität}{Düsseldorf}{}{Seminar ``Chinesische
%Phonologie", gehalten am Institut für Sprache und Information.}{}{}
%\cventry{{\footnotesize SoSe 2010}}{Seminar}{Heinrich Heine Universität}{Düsseldorf}{}{Seminar ``Sprachkontakt und
%Sprachwandel", gehalten am Institut für Sprache und Information.}{}{}
%\cventry{{\footnotesize WiSe 2009}}{Seminar}{Heinrich Heine Universität}{Düsseldorf}{}{Seminar ``Linguistische
%Rekonstruktion: Theorien und Methoden", gehalten am Institut für Sprache und Information.}{}{}
\section{Supervisor of Bachelor and Master Thesises}
\cventry{{\footnotesize 11/2013}}{Marisa Delz, Master Thesis ``A theoretical approach on automatic
loanword detection"}{Eberhard-Karls Universität}{Tübingen}{Secondary Supervisor}{}
\cventry{{\footnotesize 06/2013}}{Yang Liu, Bachelor Thesis ``Variation der Numeralklassifikation im
Chinesischen [Variation of numeral classification in
Chinese]"}{Philipps-Universität}{Marburg}{Secondary Supervisor}{}
\cventry{{\footnotesize 10/2010}}{Isabell Haller, Bachelor Thesis ``Modelle der genetischen
Sprachklassifikation: Bäume, Wellen, Netze [Models of genetic language classification: Trees, Waves,
Networks]"}{Heinrich Heine Universität}{Düsseldorf}{Supervisor}{}
\section{Organisation}
\cventry{{\footnotesize 06/02/2014}}{Demo and poster session of the section on computational
linguistics organized as part of the 36th Meeting of the German Society for Linguistics (Deutsche
Gesellschaft für Sprachwissenschaft)}{Philipps-Universität}{Marburg}{}{Participant of the
organisational board, together with Thomas Mayer and
Nathalia Levshina.}{}{}
\section{Further Occupations and Activities}
\cventry{{\footnotesize 09/2001--08/2002}}{Civil Service}{Children's Circus
Upsala}{Saint Petersburg}{}{Assistant and juggling trainer in the social project ``Upsala Cirk
[Upsala Circus]".}
\section{Scholarships and Awards}
\cventry{{\footnotesize 03/02/2014}}{Best Dissertation of the Philosophical Faculty in 2013}{Heinrich
Heine Universität}{Düsseldorf}{}{Annual prize (2500 Euros) awarded by the Philosophical Faculty of
 Heinrich Heine Universität Düsseldorf.}{}
\cventry{{\footnotesize 11-13/08/2013}}{Young Scholars Symposium}{University of
Washington}{Seattle}{}{Invitation of the ``LFK
Society for Chinese Linguistics" to take part in the fully sponsored LFK Young Scholars Symposium.}{ }
\cventry{{\footnotesize 09/2007--01/2008}}{Semester Scholarship}{German Academic Exchange Service}{Bonn}{}{
Scholarship for one semester at Fúdàn University Shànghǎi.}{}
\cventry{{\footnotesize 09/2005--08/2006}}{Exchange Scholarship}{Freie Universität Berlin / Fúdàn
Universität Shanghai}{Berlin / Shanghai}{}{Scholarship of Freie
Universität Berlin in cooperation with Fúdàn University Shànghǎi for two semesters of Chinese
language studies at Fúdàn University Shànghǎi.}{}
%\cventry{{\footnotesize 20.08.2005}}{Lilalu Zirkuspreis 2005}{}{München}{\em Zweiter
%Platz in der Kategorie ``Erwachsene / Amateure"}{}{}
\cventry{{\footnotesize 23/10/2004}}{Young Talents of Cabaret Competition}{Sophienhof}{Kiel}{\em
Second Prize}{Second prize (500 Euros) for a ``Funny Juggling Performance with Rings".}{}
\cventry{{\footnotesize 07/06/2001}}{Federal Competition ``Jugend musiziert"}{Federal Ministry for Family Affairs, Senior
Citizens, Women and Youth}{Hamburg}{Second Prize}{\em Second Price, Category ``Plucked Instruments /
Trio" (together with Katun Luc and Katharina
Dornieden.}{}{}{}
 
\section{Language Skills}
\cvlanguage{{\footnotesize German}}{native speaker}{}
\cvlanguage{{\footnotesize Russian}}{fluent}{}
\cvlanguage{{\footnotesize Chinese}}{fluent} {HSK: B (7)\textcolor{white}{....}}
\cvlanguage{{\footnotesize English}}{fluent}{TOEFL iBT: 107\textcolor{white}{....}}
\cvlanguage{{\footnotesize Latin}}{good knowledge}    {Major Latinum\textcolor{white}{....}}
\cvlanguage{{\footnotesize Old Greek}}{good knowledge}    {Graecum\textcolor{white}{....}}
\cvlanguage{{\footnotesize Sanskrit}}{good knowledge}{}
\cvlanguage{{\footnotesize Swedish}}{basic knowledge}{}
\cvlanguage{{\footnotesize Danish}}{basic knowledge}{}
\cvlanguage{{\footnotesize French}}{basic knowledge}{}

 
\section{Computer Skills}
\cvlanguage{{\footnotesize Languages}}{Python, R, C{\ttfamily ++}, AWK, BASH (Unix Shell), PHP,
SQL, JavaScript}{}
\cvlanguage{{\footnotesize Formatting}}{\LaTeX{},
Microsoft Word, LibreOffice, HTML/CSS}{}
\cvlanguage{{\footnotesize Grafics}}{\hspace{0.0cm}PSTricks, GIMP, InkScape}{}
\cvlanguage{{\footnotesize
Operating Systems}}{\hspace{0.0cm}Linux, Windows}{}

\section{Publications}
\input{papers}
\end{document}
