

\subsection{Papers to appear}
 
\begin{itemize}
\item[] Geisler, Hans and List, Johann-Mattis (forthcoming): \textbf{Beautiful trees on unstable ground. Notes on the data problem in lexicostatistics}. In Hettrich, Heinrich (ed)  \textit{Die Ausbreitung des Indogermanischen. Thesen aus Sprachwissenschaft, Archäologie und Genetik} Reichert: Wiesbaden. .

\end{itemize}
\subsection{Papers from 2014}
 
\begin{itemize}
\item[] List, Johann-Mattis; Nelson-Sathi, Shijulal; Martin, William and Geisler, Hans (2014): \textbf{Using phylogenetic networks to model Chinese dialect history}. \textit{Language Dynamics and Change}} 4.2. . 222–252.

\item[] List, J.-M. (2014): \textbf{Sequence comparison in historical linguistics}. Düsseldorf University Press: Düsseldorf.

\item[] Mayer, Thomas; List, Johann-Mattis; Terhalle, Anselm and Urban, Matthias (2014): \textbf{An interactive visualization of cross-linguistic colexification patterns}. In \textit{Visualization as added value in the development, use and evaluation of Linguistic Resources. Workshop organized as part of the International Conference on Language Resources and Evaluation}. . 1-8.

\item[] List, J.-M. and Prokić, J. (2014): \textbf{A benchmark database of phonetic alignments in historical linguistics and dialectology.}. In \textit{Proceedings of the Ninth International Conference on Language Resources and Evaluation}. . 288-294.

\item[] List, J.-M. (2014): \textbf{Investigating the impact of sample size on cognate detection}. \textit{Journal of Language Relationship}} 11. . 91-101.

\item[] List, Johann-Mattis; Nelson-Sathi, Shijulal; Geisler, Hans and Martin, William (2014): \textbf{Networks of lexical borrowing and lateral gene transfer in language and genome evolution}. \textit{Bioessays}} 36.2. . 141-150.

\end{itemize}
\subsection{Papers from 2013}
 
\begin{itemize}
\item[] Shijulal Nelson-Sathi; Popa, Ovidiu; List, Johann-Mattis; Geisler, Hans; Martin, William F. and Dagan, Tal (2013): \textbf{Reconstructing the lateral component of language history and genome evolution using network approaches}. In Heiner Fangerau et al. (eds)  \textit{Classification and evolution in biology, linguistics and the history of science. Concepts – methods – visualization.} Franz Steiner Verlag: Stuttgart. . 163-180.

\item[] Lopez, P.; List, J.-M. and Bapteste, E. (2013): \textbf{A preliminary case for exploratory networks in biology and linguistics: the phonetic network of Chinese words as a case-study}. In Heiner Fangerau et al. (eds)  \textit{Classification and evolution in biology, linguistics and the history of science. Concepts – methods – visualization.} Franz Steiner Verlag: Stuttgart. . 181-196.

\item[] Geisler, H. and List, J.-M. (2013): \textbf{Do languages grow on trees? The tree metaphor in the history of linguistics}. In Heiner Fangerau et al. (eds)  \textit{Classification and evolution in biology, linguistics and the history of science. Concepts – methods – visualization.} Franz Steiner Verlag: Stuttgart. . 111-124.

\item[] List, Johann-Mattis and Moran, Steven (2013): \textbf{An open source toolkit for quantitative historical linguistics}. In \textit{Proceedings of the ACL 2013 System Demonstrations}. . 13-18.

\item[] List, Johann-Mattis; Terhalle, Anselm and Urban, Matthias (2013): \textbf{Using network approaches to enhance the analysis of cross-linguistic polysemies}. In \textit{Proceedings of the 10th International Conference on Computational Semantics -- Short Papers}. . 347-353.

\end{itemize}
\subsection{Papers from 2012}
 
\begin{itemize}
\item[] List, Johann-Mattis (2012): \textbf{Improving phonetic alignment by handling secondary sequence structures}. In \textit{Computational approaches to the study of dialectal and typological variation. Working papers submitted for the workshop organized as part of the ESSLLI 2012}. .

\item[] List, Johann-Mattis (2012): \textbf{LexStat. Automatic detection of cognates in multilingual wordlists}. In \textit{Proceedings of the EACL 2012 Joint Workshop of Visualization of Linguistic Patterns and Uncovering Language History from Multilingual Resources}. . 117-125.

\item[] List, Johann-Mattis (2012): \textbf{SCA. Phonetic alignment based on sound classes}. In Slavkovik, Marija and Lassiter, Dan (eds)  \textit{New directions in logic, language, and computation} Springer: Berlin and Heidelberg. . 32-51.

\item[] List, Johann-Mattis (2012): \textbf{Multiple sequence alignment in historical linguistics. A sound class based approach}. In \textit{Proceedings of ConSOLE XIX}. . 241-260.

\end{itemize}
\subsection{Papers from 2011}
 
\begin{itemize}
\item[] Holman, Eric. W.; Brown, Cecil H.; Wichmann, Søren; M\"uller, Andr\'e; Velupillai, Viveka; Hammarstr\"om, Harald; Sauppe, Sebastian; Jung, Hagen; Bakker, Dik; Brown, Pamela; Belyaev, Oleg; Urban, Matthias; Mailhammer, Robert; List, Johann-Mattis and Egorov, Dimitry (2011): \textbf{Automated dating of the world's language families based on lexical similarity}. \textit{Current Anthropology}} 52.6. . 841-875.

\item[] Nelson-Sathi, Shijulal; List, Johann-Mattis; Geisler, Hans; Fangerau, Heiner; Gray, Russell D.; Martin, William and Dagan, Tal (2011): \textbf{Networks uncover hidden lexical borrowing in Indo-European language evolution}. \textit{Proceedings of the Royal Society B}} 278.1713. . 1794-1803.

\end{itemize}
\subsection{Papers from 2010}
 
\begin{itemize}
\item[] List, Johann-Mattis (2010): \textbf{Phonetic alignment based on sound classes. A new method for sequence comparison in historical linguistics}. In \textit{Proceedings of the 15th Student Session of the European Summer School for Logic, Language and Information}. . 192-202.

\item[] Wichmann, Søren; Holman, Eric W.; Müller, André; Velupillai, Viveka; List, Johann-Mattis; Belyaev, Oleg; Urban, Matthias and Bakker, Dik (2010): \textbf{Glottochronology as a heuristic for genealogical language relationships}. \textit{Journal of Quantitative Linguistics}} 17.4. . 303-316.

\end{itemize}
\subsection{Papers from 2009}
 
\begin{itemize}
\item[] List, Johann-Mattis (2009): \textbf{Sprachvariation im modernen Chinesisch}. \textit{CHUN -- Chinesischunterricht}} 24. . 123-140.

\end{itemize}
\subsection{Papers from 2008}
 
\begin{itemize}
\item[] List, J.-M. (2008): \textbf{The validity of reconstruction systems}. Research Proposal.

\item[] List, Johann-Mattis (2008): \textbf{The puzzling case of Boshan tone sandhi}. Working paper.

\item[] List, Johann-Mattis (2008): \textbf{Resultativkomposita im Chinesischen [Resultative compounds in Chinese]}. Summary.

\item[] List, Johann-Mattis (2008): \textbf{Rekonstruktion der Aussprache des Mittel- und Altchinesischen. Vergleich der Rekonstruktionsmethoden der indogermanischen und der chinesischen Sprachwissenschaft [Reconstruction of the pronunciation of Middle and Old Chinese. Comparison of reconstruction methods in Indo-European and Chinese linguistics]}. Magister thesis. Freie Universität Berlin.

\end{itemize}
\subsection{Papers from 2007}
 
\begin{itemize}
\item[] List, Johann-Mattis (2007): \textbf{Typology and linguistic reconstruction}. Working paper.

\item[] List, Johann-Mattis (2007): \textbf{The derivational character of the Chinese writing system}. Working paper.

\item[] List, Johann-Mattis (2007): \textbf{Osnovy rekonstrukcii srednekitajskogo i drevnekitajskogo jazykov [Introduction to the reconstruction of Middle and Old Chinese]}. Summary.

\item[] List, Johann-Mattis (2007): \textbf{\textit{Cóng Éwén de jiǎodù lái kàn pànduàn dòngcí "shì" de qǐyuán yǔ yǎnbiàn} 从俄文的角度来看判断动词“是”的起源与演变 [Origin and change of the Chinese copula shì from a Russian perspective]}. Working paper.

\end{itemize}